Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce

### 2019-09-19 Paper.tex
dsadsadas

\keywords{MapReduce, Fault tolerance, Arbitrary failure, Data locality}
\maketitle

@@

Finally, we remember that our prototype's source code is fully available on GitHub\footnote{\url{https://github.com/AndreaG93/SDCC-Project}}, famous web-based hosting service for version control using \texttt{git}; we remind that \LaTeX\ source code of this paper is available too\footnote{See \url{https://github.com/AndreaG93/SDCC-Project-Report}}.

@@

In order to properly describe how our algorithm can tolerate arbitrary faults and to exploit data locality, it is necessary to describe its architecture. To do that, in this section we start making some very important assumptions.

Our system is composed by a \textit{set of distributed processes}, every of which run on different hosts in a same data-center.

We assume that our system runs \textit{asynchronously}, that is no assumptions about process execution speeds or message delivery times are made; therefore we can normally use timeouts to state that a process has crashed although, occasionally, such conclusion is false \cite{SDCC}.

All processes are connected by \textit{reliable channels}, so no messages are lost, duplicated or corrupted; that feature is guaranteed by TCP connections. In our prototype, all system's processes use RPC protocol in order to interact with each other.

@@

In this paper, we take for granted reader's knowledge of the MapReduce framework and main aspects of Hadoop  framework.

@@

\subsection{Primary Process}
At this point, is necessary to make some clarifications about PP's features.

Unlike Hadoop, according to which \textit{JobTracker} process is assumed always correct, we have design our system believing that the host where PP is running may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents for us a \textit{single point of failure}.

Therefore, to ensure an high system availability, adopting the same design used in Apache Mesos\textsuperscript{TM}\ \footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, our system architecture is based on multiple PP backup copies run on \textit{different machines} (in our prototype, on different EC2 instances); using a leader election algorithm, is possible to elect one of these copies as leader, becoming the \textit{Leader Primary Process} (LPP), while all the others remain on stand-by. Using this approach, is possible to manage PP crash failure: when current LPP fails, a backup copy is promoted to become the new leader.

>>>>

\keywords{MapReduce, Arbitrary Fault Tolerance, Locality Awareness, Speculative Execution, Leader Election Algorithm, Deferred Execution}
\maketitle

@@

Finally, we remember that our prototype's source code is fully available on GitHub\footnote{\url{https://github.com/AndreaG93/SDCC-Project}}, famous web-based hosting service for version control using \texttt{git}; we remind that \LaTeX\ source code of this paper is available too\footnote{See \url{https://github.com/AndreaG93/SDCC-Project-Report}}. In this paper, we take for granted reader's knowledge of the MapReduce framework and part of Hadoop framework.

@@

In order to properly describe how our system can achieve a certain level of arbitrary fault tolerance without unduly compromising performance, let's start making some very important assumptions.

We have designed our cloud application as a \textit{set of processes}, every of which have to run on \textit{different} servers with a certain replication degree in order to achieve a certain level of arbitrary fault tolerance. Available processes are not all the same but several kind of these exist with its own features and aims which we will describe them in detail in following section; in fact, we distinguish three process type: \textit{Client Process}, \textit{Primary Process} (PP) and \textit{Worker Process} (WP);

We assume that our system runs \textit{asynchronously}, that is no assumptions about process execution speeds or message delivery times are made; therefore we can normally use a time-out to state that a process has crashed although, occasionally, such conclusion is false \cite{SDCC}.

We assume that all processes are connected by \textit{reliable channels}, that is no messages are lost, duplicated or corrupted. In our prototype that feature is guaranteed  by the use of Go implementation of RPC\footnote{\url{https://golang.org/pkg/net/rpc/}} (\textit{Remote Procedure Call}) which is based on TCP connections. Mostly all RPC calls, except those made by the client process, are asynchronous\footnote{Although Go's \texttt{rpc} package provides its own support for RPC asynchronous calls, we have  preferred to adopt an equivalent approach based on properly used goroutine and channels.}.

@@

@@

\subsection{Primary Process}

Most of the activities carried out by a Primary Process (PP) are very similar to those performed by \textit{JobTracker} process used in Apache Hadoop framework. These activities including \textit{Map-Task} or \textit{Reduce-Task} scheduling, pre-signed URLs generation, managing of worker nodes replies, clients request managing and so on.

However unlike Apache Hadoop framework, according to which \textit{JobTracker} process is assumed always correct, we have design our system believing that the host where PP is running may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents for us a \textit{single point of failure}. Therefore, to ensure an high system availability, inspired by Apache Mesos\textsuperscript{TM}\ architecture\footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, we have adopt a design according to which multiple PP backup copies exist and they run on \textit{different machines} (in our prototype, on different EC2 instances); using a leader election algorithm, is possible to elect one of these copies as leader, becoming the \textit{Leader Primary Process} (LPP), while all the others remain on stand-by. Using this approach, is possible to manage PP crash failure: when current LPP fails, a backup copy is promoted to become the new leader.
